Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-31 Talks/FU-Berlin/talk-part-1.tex
Add Gaunilo
update for FU talk

\hskip-.5em
\ldots\rotatebox[origin = bl,width = 0mm]{65}{\textcolor{blue}{Anselm v. C.}} \hskip-2.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Th. Aquinas}}  \hskip-2.3em
\ldots\ldots   \rotatebox[origin = bl]{65}{\textcolor{blue}{Descartes}} \hskip-1.7em
               \rotatebox[origin = bl]{65}{\textcolor{blue}{Spinoza}} \hskip-1.3em
               \rotatebox[origin = bl]{65}{\textcolor{blue}{Leibniz}}  \hskip-1.2em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Hume}}  \hskip-1em
          \rotatebox[origin = bl]{65}{\textcolor{red}{Kant}}  \hskip-.8em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{blue}{Hegel}}  \hskip-1.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Frege}}  \hskip-1.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{blue}{Hartshorne}} \hskip-1.9em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{Malcolm}}  \hskip-1.4em
          \rotatebox[origin = bl]{65}{\textcolor{red}{Lewis}}  \hskip-1em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{Plantinga}}  \hskip-1.6em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{G\"odel}}   \hskip-1.2em
\ldots \\[1em]

@@

\begin{frame}{Introduction} \large
Main challenge: \hfill No provers for \emph{Higher-order Modal Logic\/} (\textcolor{red}{HML}) \\[1em]

Our solution: \hfill Embedding in \emph{Higher-order Classical Logic\/} (\textcolor{blue}{HOL}) \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

What we did \textcolor{blue}{(rough outline for remaining
  presentation!)}: \\

\begin{itemize}
\item[A:] Pen and paper: \hfill detailed natural deduction proof 
\item[B:] Formalization: \hfill in classical higher-order logic (\textcolor{blue}{HOL})
\item[] Automation: \hfill theorem provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] Consistency: \hfill model finder \textsc{Nitpick (Nitrox)} 
\item[C:] Step-by-step verification: \hfill proof assistant \textsc{Coq} 
\item[D:] Automation \& verification: \hfill proof assistant \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss this later!}
\end{frame}

>>>>

\hskip-.5em
\ldots\rotatebox[origin = bl,width = 0mm]{65}{\textcolor{blue}{Anselm v. C.}} \hskip-2.3em
          \rotatebox[origin = bl]{65}{\textcolor{red}{Gaunilo}} \hskip-1.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Th. Aquinas}}  \hskip-2.3em
\ldots\ldots   \rotatebox[origin = bl]{65}{\textcolor{blue}{Descartes}} \hskip-1.7em
               \rotatebox[origin = bl]{65}{\textcolor{blue}{Spinoza}} \hskip-1.3em
               \rotatebox[origin = bl]{65}{\textcolor{blue}{Leibniz}}  \hskip-1.2em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Hume}}  \hskip-1em
          \rotatebox[origin = bl]{65}{\textcolor{red}{Kant}}  \hskip-.8em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{blue}{Hegel}}  \hskip-1.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{red}{Frege}}  \hskip-1.3em
\ldots  \rotatebox[origin = bl]{65}{\textcolor{blue}{Hartshorne}} \hskip-1.9em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{Malcolm}}  \hskip-1.4em
          \rotatebox[origin = bl]{65}{\textcolor{red}{Lewis}}  \hskip-1em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{Plantinga}}  \hskip-1.6em
          \rotatebox[origin = bl]{65}{\textcolor{blue}{G\"odel}}   \hskip-1.2em
\ldots \\[1em]

@@

\begin{frame}{Introduction} \large
\hskip-1em Challenge: \hfill No provers for \emph{Higher-order Quantified Modal Logic\/} (\textcolor{red}{QML}) \\[1em]

\hskip-1em Our solution: \hfill Embedding in \emph{Higher-order Classical Logic\/} (\textcolor{blue}{HOL}) \\
\,\hfill {\small [Benzm\"ullerPaulson, Logica Universalis, 2013]} \\[2em]

\hskip-1em What we did \textcolor{blue}{(rough outline for remaining
  presentation!)}: \\

\begin{itemize}
\item[A:] Pen and paper: \hfill detailed natural deduction proof 
\item[B:] Formalization: \hfill in classical higher-order logic (\textcolor{blue}{HOL})
\item[] Automation: \hfill theorem provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] Consistency: \hfill model finder \textsc{Nitpick (Nitrox)} 
\item[C:] Step-by-step verification: \hfill proof assistant \textsc{Coq} 
\item[D:] Automation \& verification: \hfill proof assistant \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
\hskip-1em  Did we get any new results? \hfill  \textcolor{red}{Yes --- let's discuss this later!}
\end{frame}
